Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-26 WSSSPE1_report/WSSSPE1_summary_report.tex
fixed a couple of minor things in first keynote section

Bourne's keynote presentation was entitled ``A Recipe for Sustainable
Software,'' developed based on his experiences.  He emphasized that
sustainability for software ``does not just mean more money from
Government'' (see also Section~\ref{sec:cross-cutting}).  Other
factors to consider, he mentioned, include costs of production, ease
of maintenance, community involvement, and distribution channels.

In places, Bourne said, development in science has improved thanks to
open source and GitHub~\cite{github-web}, but for the most part
remains arcane. He argued that we can learn much from the App Store
model about interfaces, ratings, and so on. He also mentioned
BioJava~\cite{biojava-web} and Open Science Data Cloud~\cite{osdc-web}
as distribution channels.  On a related note, Bourne observed a common
evolutionary pathway for computational biology projects, from data
archive to analytics platform to educational use, and suggested that
use of scientific software for outreach might be the final step.

Bourne shared with the audience a few real challenges he
encountered. First, also an anecdote, he has looked into
reproducibility in computational biology, but has concluded that ``I
have proved I cannot reproduce research from my own
lab.''~\cite{Veretnik}

@@

He then presented the usual arguments on directly valuing software as
a research output alongside papers. Readers will be familiar with this
debate.  An interesting reference provided by him
is~\cite{peer-review-code}, which explores involving software
engineers in the review process of scientific code.

@@

He concluded with a reference to his paper~\cite{bourne_ten} and
argued that computational scientists ``have a responsibility to
convince their institutions, reviewers, and communities that software is
scholarship, frequently
more valuable than a research article,'' a point with which we strongly agree.

>>>>

Bourne's keynote presentation was entitled ``A Recipe for Sustainable
Software'', and developed based on his experiences.  He emphasized that
sustainability for software ``does not just mean more money from
Government'' (see also Section~\ref{sec:cross-cutting}).  Other
factors to consider, he mentioned, include costs of production, ease
of maintenance, community involvement, and distribution channels.

In places, Bourne said, development in science has improved thanks to
open source and hosting services like GitHub~\cite{github-web}, but for the most part
remains arcane. He argued that we can learn much from the App Store
model about interfaces, ratings, and so on. He also mentioned
BioJava~\cite{biojava-web} and Open Science Data Cloud~\cite{osdc-web}
as distribution channels.  On a related note, Bourne observed a common
evolutionary pathway for computational biology projects, from data
archive to analytics platform to educational use, and suggested that
use of scientific software for outreach might be the final step.

Bourne shared with the audience a few real challenges he
encountered. First, also an anecdote, he has looked into
reproducibility in computational biology, but has concluded that ``I
have proved I cannot reproduce research from my own
lab''~\cite{Veretnik}.

@@

He then presented arguments on directly valuing software as
a research output alongside papers, a common discussion within this field.
An interesting reference provided by him
is~\cite{peer-review-code}, which explores involving software
engineers in the review process of scientific code.

@@

He concluded with a reference to his paper~\cite{bourne_ten} and
argued that computational scientists ``have a responsibility to
convince their institutions, reviewers, and communities that software is
scholarship, frequently
more valuable than a research article,'' a point with which all authors
strongly agree.
